Universal Anonymous Signatures

### 2022-06-18 prism-backend/research/gsac/app-model-related.tex
UAS => MPS.

>>>>

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable with a restriction of \UAS. Concretely, by restricting to
a system with one issuer and one opener, one credential per user, one attribute
per credential (the user secret key), $\fissue^1$ issuance functions, and
\feval functions that only use the $\yeval^1$ output -- which we denote with
$\feval^{\yeval^1}$.

There are some differences, though. On the one hand, our signature anonymity
property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
Their privacy-1 variant is the traditional anonymity property of group
signatures, in which the opener is honest and the adversary can call the opening
oracle except for challenge signatures. In their privacy-2 variant, the opener
is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
(getting ther \osk), but the challenge signatures must have been generated using
the key of an uncorrupted opener; still, \adv~can call the open oracle for
challenge signatures, as long as they have the same \yinsp value. We believe
that these differences are mostly of theoretical interest, though, and it does
not seem hard to move from one to the other \todo{check}. In practice,
what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
in MPS) that has too much granularity in their ranges, will lead to a barely
private system. This is a known issue, for instance, in functional encryption
\needcite.

On the other hand, our issuance-related properties (issuance anonymity and
issuance unforgeability) are unachievable by MPS. Issuance anonymity simply does
not make sense in MPS, as it only supports one credential (without attributes)
per user. Issuance unforgeability does not make sense either, since there are no
configurable issuance policies in MPS -- instead, they have the fixed policy of
``proving knowledge of a user secret key''. These extensions are not trivial
from a theoretical point of view, and also have a big impact in the practicality
of the resulting system. Also, MPS does not include verifiable openings. While
this is easy to add, we consider it to be essential, given that the proposed
generalization of opening allows the opener to output ``any value''. Hence, the
need to ensure that the produced value is the legitimate one, seems to be more
necessary than ever. Finally, our \feval function is a generalization of $F$ in
MPS, as it allows two outputs: one will be returned in the clear along with the
signature, and the other will be encrypted. Still both computations are proved
correct. Making part of the output unencrypted allows implementing very useful
variants such as anonymous credentials with selective disclosure -- as shown
before.

For the model of MPS schemes, we refer to the original paper \needcite.

\subsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^1,\feval^{\yeval^1},\finsp^\ast)$-restriction of
\CUASGen with only one issuer and opener, one credential per user, and one
attribute per credential (the user secret key), implements an MPS scheme where
$F=\feval^{\yeval^1}$ and $G=\finsp^\ast$. The restriction to one credential per
user, and one attribute per credential, can be done as in
\appref{sapp:related-models-gs}. Finally, note that, in MPS, $G$ is further
parameterized with a value $j$, which essentially is the result of applying $F$
to the message and signer identity, and is not leaked to the opener nor any
other third party. The equivalent in \UAS is the $\yeval^1$ value, which is
encrypted with a single-use key pair, and is an input of \yinsp.

\paragraph{Security of \CUASMPS.} %
As stated, we restrict to privacy-1 of MPS. Unforgeability-1 in MPS is
equivalent to sign unforgeability in \UAS. Unforgeability-2 in MPS is
equivalent to non-frameability in \UAS. Finally note that, in UAS, we do not
explicitly model extractability, but rather make it an inherent requirement in
the unforgeability and non-frameability definitions. Thus, our \CUASMPS
construction also ensures MPS-extractability.

\begin{theorem}[Privacy-1 of \CUASMPS]
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
  according to \needcite.
\end{theorem}

\begin{proof}
  The proof is direct, by observing that the models are equivalent.

  First, note that, in MPS the adversary is required to output a function $F$,
  challenge message, and a pair of user secret keys and witnesses (in \UAS, the
  witnesses are the credentials). This is precisely what \CHALb requires as
  input in our \UAS modelling.

  Next, in MPS, validity of the output of $F$ is checked. In MPS, this
  translates to checking that $F$ does not ouptut $0$. In UAS, this is checked
  in the \SIGN and \CHALb oracles, which abort if the output produced by \feval
  does not belong in \rngfeval -- a well defined set of acceptable outputs by
  the chosen \feval.

  The MPS adversary is then allowed to make more oracle queries, and outputs a
  response bit. Just as in \UAS. Thus, if \CUASMPS satisfies signature
  anonymity, it is also an MPS scheme satisfying privacy-1.  
  % 
  \qed
\end{proof}

\begin{theorem}[Extractability of \CUASMPS]
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, then it is an extractable MPS scheme.
\end{theorem}

\begin{proof}
  The proof is direct, as the conditions checked in the extractability
  experiment in MPS are also checked in the signature unforgeability experiment
  for \UAS.

  Concretely, \Verify must accept the signature, and the ouptut of \feval and
  \finsp, computed with the values extracted by \ExtractSign, must respectively
  match those output by the adversary (for \feval), and computed honestly by the
  signature unforgeability (for \finsp).  
  \qed
\end{proof}

\begin{theorem}[Unforgeability-1 of \CUASMPS]
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
  defined in \needcite.
\end{theorem}

\begin{proof}
  For an MPS scheme to satisfy type-1 unforgeability, it has to be extractable.
  This is directly satisfied by signature unforgeability in \UAS.
  %
  Next, the adversary wins in the unforgeability-1 MPS experiment if it manages
  to produce a signature that has not been produced via a call to their \SIGN
  oracle, nor it can be associated to an corrupt user. Indeed, if that happens,
  then such adversary can be used to build an adversary winning the signature
  unforgeability game against \CUASMPS, through winning condition at line 12 --
  as \IdentifyUK does not return 1 for any known \uid. Thus, if \CUASMPS has
  signature unforgeability, it also satisfies unforgeability-1 of MPS schemes.
  %
  \qed
\end{proof}

\begin{theorem}[Unforgeability-2 of \CUASMPS]
  If the base \CUASGen construction has non-frameability according to
  \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
  defined in \needcite.
\end{theorem}

\begin{proof}
  For an MPS scheme to have type-2 unforgeability, it has to be extractable.
  This is directly satisfied by non-frameability in UAS (a similar reasoning
  as for signature unforgeability and extractability applies here).
  %
  Next, in MPS, the adversary wins if the produced signature has not been
  output by the \SIGN oracle, but Extract outputs the identifier of an honest
  user. This is the same check done in lines 9 and 10 of the non-frameability
  game in \UAS. Therefore, if \CUASMPS satisfies non-frameability as defined in
  \defref{def:frame-uas}, it also satisfies type-2 unforgeability in MPS.
  \qed
\end{proof}
